---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# deflator

<!-- badges: start -->
<!-- badges: end -->

The deflator is a demonstration of how to create a simple package.  It has one
function, `flate_gdp()`, for inflating or deflating UK prices by GDP.  It also
has one dataset, `gdp_deflator`, which is a data frame of year-on-year inflation
rates published on
[GOV.UK](https://www.gov.uk/government/statistics/gdp-deflators-at-market-prices-and-money-gdp-march-2019-quarterly-national-accounts).

## Installation

You can install from [github](https://github.com/nacnudus/deflator) with:

```r
devtools::install_github("deflator")
```

## Example

Inflate £100 from 2017 prices to 2019 prices, by GDP.

```{r inflate}
library(deflator)
flate_gdp(100, 2017, 2019)
```

Go back again: deflate £103 from 2019 prices to 2017 prices, by GDP.

```{r deflate}
flate_gdp(103.9335, 2019, 2017)
```
